The ChEMBL database as Linked Open Data

### 2013-03-26 article.tex
emphasise that the sparql query is a template and cannot therefore be directly run
new to novel

Using the SPARQL end point, it is easy to integrate data from ChEMBL into other web resources, such as CitedIn (http://www.citedin.org)~\cite{CitedIn2011}.
While the impact of a scientific publication is traditionally measured by frequency of citation in subsequent publications, this
narrowly defined calculation increasingly fails to capture the true reach of a paper. CitedIn was developed to make scientific
impact more visible and more accurate by providing insight into where published work is being cited online in a variety of public
resources, as listed on the CitedIn website~\cite{CitedResources}.
ChEMBL contains many literature references. The SPARQL endpoint is queried by CitedIn and the results are presented to its users.
Figure~\ref{fig:citedin} shows the results for the Nature paper by Gamo presenting the malaria structures~\cite{Gamo2010}
which is cited as the reference for a large number of activity datapoints and compounds in ChEMBL.
Counting all objects that reference this paper is done by the following SPARQL query:

@@

This paper shows the evolution of the ChEMBL-RDF resource in standardizing access to the
ChEMBL data in a machine-readable manner using semantic web technologies. We showed here
that the conversion into RDF allows a number of new integrations with other resources.
It should be clear that these applications can be made using other technologies too, but
using the RDF standards it is easier to implement them. More importantly, the solutions
will be generally applicable to any system using these open standards. However, a number
of choices need discussion.

>>>>

Using the SPARQL end point, it is easy to integrate data from ChEMBL into other web resources, such as CitedIn (http://www.citedin.org)~\cite{CitedIn2011}.
While the impact of a scientific publication is traditionally measured by frequency of citation in subsequent publications, this
narrowly defined calculation increasingly fails to capture the true reach of a paper. CitedIn was developed to make scientific
impact more visible and more accurate by providing insight into where published work is being cited online in a variety of public
resources, as listed on the CitedIn website~\cite{CitedResources}.
ChEMBL contains many literature references. The SPARQL endpoint is queried by CitedIn and the results are presented to its users.
Figure~\ref{fig:citedin} shows the results for the Nature paper by Gamo presenting the malaria structures~\cite{Gamo2010}
which is cited as the reference for a large number of activity datapoints and compounds in ChEMBL.
Counting all objects that reference this paper is done by the following SPARQL query template:

@@

This paper shows the evolution of the ChEMBL-RDF resource in standardizing access to the
ChEMBL data in a machine-readable manner using semantic web technologies. We showed here
that the conversion into RDF allows a number of novel integrations with other resources.
It should be clear that these applications can be made using other technologies too, but
using the RDF standards it is easier to implement them. More importantly, the solutions
will be generally applicable to any system using these open standards. However, a number
of choices need discussion.
